Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-19 2016_ICML/cmrs.tex
Adding URL of code

In the first experiment, we conduct a similar analysis as \citet[Section
3.1]{hennig_entropy_2012}: we compare different algorithms on a number of
single-task functions sampled from a generative model, namely from the same GP-based model
that is used by the optimization internally as surrogate model. This precludes
model-mismatch issues and unwanted bias which could be introduced by resorting
to common hand-crafted test functions. More specifically, we choose the
parameter space to be the 2-dimensional unit domain $\mathcal{X} = [0, 1]^2$ and generate test
functions by sampling $250$ function values jointly from a GP with an isotropic RBF kernel
of length scale $l = 0.1$ and unit signal variance. A GP is
fitted to these function values and the resulting posterior mean is used as the
test function. Moreover, Gaussian noise with standard deviation $\sigma =
10^{-3}$ is added to each observation. The GP used as surrogate model in the optimizer employed the same 
isotropic RBF kernel with fixed, identical hyperparameters. 
In order to isolate effects of the different acquisition functions from effects of different
recommendation mechanisms, we used the point which maximizes the GP posterior
mean as recommendation $\mathbf{\tilde x}_N$ regardless of the employed acquisition function.
All algorithms were tested on the same
set of $250$ test functions, and we used $n_f=1000$, $n_r=25$, and $n_y=51$.
We do not provide error-bars on the estimates as the data sets have no parametric distribution. 
However, we provide additional histograms on the regret distribution.

>>>>

In the first experiment\footnote{Source code for replicating the reported experiment
is available under \url{https://github.com/jmetzen/bayesian_optimization}.}, 
we conduct a similar analysis as \citet[Section
3.1]{hennig_entropy_2012}: we compare different algorithms on a number of
single-task functions sampled from a generative model, namely from the same GP-based model
that is used by the optimization internally as surrogate model. This precludes
model-mismatch issues and unwanted bias which could be introduced by resorting
to common hand-crafted test functions. More specifically, we choose the
parameter space to be the 2-dimensional unit domain $\mathcal{X} = [0, 1]^2$ and generate test
functions by sampling $250$ function values jointly from a GP with an isotropic RBF kernel
of length scale $l = 0.1$ and unit signal variance. A GP is
fitted to these function values and the resulting posterior mean is used as the
test function. Moreover, Gaussian noise with standard deviation $\sigma =
10^{-3}$ is added to each observation. The GP used as surrogate model in the optimizer employed the same 
isotropic RBF kernel with fixed, identical hyperparameters. 
In order to isolate effects of the different acquisition functions from effects of different
recommendation mechanisms, we used the point which maximizes the GP posterior
mean as recommendation $\mathbf{\tilde x}_N$ regardless of the employed acquisition function.
All algorithms were tested on the same
set of $250$ test functions, and we used $n_f=1000$, $n_r=25$, and $n_y=51$.
We do not provide error-bars on the estimates as the data sets have no parametric distribution. 
However, we provide additional histograms on the regret distribution.
